---
title: "Testing the interaction between active and passive learning"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Kyle MacDonald} \\ \texttt{kyle.macdonald@university.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@university.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "In active learning, people have the opportunity to select highly informative examples based on their current hypotheses, potentially allowing them to learn faster. But learning contexts often involve sequences that contain both active and passive learning, an interaction that we know little about. In the current work, we explore the interaction between active and passive learning in three category learrning experiments with adults. First, we replicate the active over passive learning advantage found in @markant2014better (Experiments 1a and 1b). Then, in Experiments 2 and 3 we provide direct tests of how different sequences of active/passive training modulate the effectiveness of active learning in two markedly different concept learning tasks. Across all three experiments, active training lead to better learning of the target concept. Passive-first training was more effective compared to Active-first in both Experiments 2 and 3. Our data provide evidence that active learning can be more effective once the learner is given passive experience, providing them with a better representation of the learning task." 
    
keywords:
    "active learning, category learning, replication, order effects"
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, message=F, sanitize = T)
```

```{r libraries}
source("../../analysis/helpers/useful.R")
library(langcog)
library(dplyr)
library(magrittr)
library(directlabels)
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

```{r binomial-smoother}
binomial_smooth <- function(...) {
    geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}
```

```{r data}
df <- read.csv("../../data/act-learn-all-data-tidy.csv", stringsAsFactors = F)
```

```{r data cleaning}
# Rename conditions and reorder levels of the condition factor.
df %<>% mutate(condition_long = condition,
               condition = factor(condition),
               condition_short = factor(condition),
               category_type_string = category_type,
               framing_condition_string = framing_condition,
               category_type = factor(category_type),
               odb_scale = ifelse(odb_scale == "radius_scale", "radius", 
                                  ifelse(odb_scale == "orientation_scale", "orientation",
                                         odb_scale)))

# rename levels of condition variable
levels(df$condition) <- c("AA", "AR", "RA", "RR", "YY")
df$condition <- factor(df$condition, levels = c("AA", "RA", "AR", "RR", "YY"))

# rename and reorder levels of category type variable
levels(df$category_type) <- c("Info-Integration", "Rule-Based")
df$category_type <- factor(df$category_type, levels = c("Rule-Based", "Info-Integration")) 
levels(df$framing_condition) <- c("Info-Integration", "None", "Rule-Based")

# rename levels of condition_short variable
levels(df$condition_short) <- c("A", "AR", "RA", "R", "Y")
df$condition_short <- factor(df$condition_short, levels = c("A", "RA", "AR", "R", "Y"))
```

# Introduction

Active learning describes a process where people can select what information they will learn next.\footnote{Here we focus on deliberate decisions about what to learn, as opposed to other uses of the term "active" learning (e.g., being engaged with learning materials).} This context stands in contrast to passive learning, where people receive information presented to them from the world. For example, consider a child playing with a new toy, testing to see how it works (active) compared to a child watching someone else play with the toy (passive). In both scenarios, the child sees a toy and some of its functions, but in the active context, the child has control over the sequence of incoming information.

The potential benefits of active learning have been the focus of research in education [@grabinger1995rich], machine learning [@settles2012active], and cognitive science [@castro2009human]. In their synthesis of this literature, @gureckis2012self present four "cognitive" explanations for why selecting information could improve learning outcomes: (1) selection of the most informative examples, (2) increased memory for selected examples, (3) direct knowledge of the sampling process, and (4) planning an action leads to a deeper understanding of the task. 

In the majority of these studies, researchers isolate active and passive training sets, and test which regime leads to better learning outcomes. For example, @markant2014better compared the effectiveness of active vs. passive training on the rate of participants’ learning of two category structures: a Rule-Based (RB) structure where the category boundary varied along a single dimension, and and Information-Integration (II) structure where the category boundary was defined by a linear combination of two dimensions. In the active learning condition, learners selected examples from the category; whereas in passive learning condition, the examples were generated randomly from the underlying distributions. @markant2014better found that participants in the active condition learned faster and achieved a higher overall accuracy, but this advantage only held for the less complex, Rule-Based category. 

While it is important to directly compare active and passive training, real-world learning often involve both. Returning to the example of learning about a new toy -- the child might see some functions demonstrated by others and then test for others (or vice versa) *within* the same learning context. But, we know relatively little about how different sequences of active/passive learning interact to affect learning outcomes. 

Research in education has asked a similar type of question: How does varying the order of different teaching methods affect learning? One illustrative example is the study of *Productive Failure*, where researchers find that first allowing students to struggle with the task (typically self-directed problem solving), leads to better uptake of the subsequent instruction  [@westermann2012delaying]. However, this work does not directly test how starting with instruction would affect the quality of the pre-instruction problem solving task. 

In comparison, there has been relatively little research in the cognitive sciences on different sequences of active and passive learning. In a cross-situational word learning task, @kachergis2013actively found that people who received a block of active learning before passive learning preformed better when asked to recall the newly learned words. The authors suggest that learners developed better attentional and memory strategies during the active training, which transferred to the passive training, boosting their overall acccuracy. But we do not yet know whether this "active first" advantage would generalize to other types of learning tasks.

In the current set of studies, we test how different sequences of active/passive training affect learning outcomes. In Experiments 1a and 1b, we directly replicate the active learning advantage found in @markant2014better. In Experiment 2, we build on our replication data to show that passive-first training is more effective than active-first. In Experiment 3, we find the same passive-first advantage in a novel paradigm where participants learn a more complex, heirarchical category structure. Together, the data suggest that active learning can provide an advantage over passive learning, but this advantage depends on the learners' representation of the task, which can be improved by receiving (a) more active learning or (b) an initial bout of passive learning.

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows a screenshot of the stimuli used in Experiments 1 and 2. The right panel shows examples of distributions of training stimuli shown to participants passive learning condition from the Rule-Based category and the Information-Integration category."}

grid::grid.raster(png::readPNG("figs/stimuli.png"))
```

# Experiment 1a

Experiment 1a is a direct replication of the advantage for active learning over passive learning found in @markant2014better. We tested participants' category learning for the RB category structure after receiving either active or passive training. We used the same stimuli and followed the exact procedures as the original study (described below). All of the stimuli and the experiments can be viewed and downloaded at the project page for this paper: https://kemacdonald.github.io/Act-Learn/. 

```{r exp1a-replication-data}
df_rep <- df %>% 
    filter(experiment == "replication_1a", 
           condition_short %in% c("A","R"), 
           category_type == "Rule-Based")
```

```{r rep1a-acc-computation}
ms_rep <- df_rep %>%
    filter(trial_type == "test") %>%
    group_by(condition_short, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))

ms_rep_block <- df_rep %>%
    filter(trial_type == "test") %>%
    group_by(condition_short, category_type, block) %>%
    summarise(mean_accuracy = mean(correct, na.rm=T),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))

ss_rep <- df_rep %>%
    filter(trial_type == "test") %>%
    group_by(condition_short, category_type, subids, experiment) %>%
    summarise(mean_accuracy = mean(correct, na.rm=T),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

```{r exp1a_t-test}
rep1a_t_test <- t.test(mean_accuracy ~ condition_short, var.equal=TRUE, 
                       data=filter(ss_rep, experiment == "replication_1a"))
```

```{r exp1a_acc_plot, fig.env = "figure*", fig.pos = "t", fig.width=5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows overall accuracy performance for the Active and Passive training conditions. The right panel shows participants' accuracy across each of the six blocks in the experiment. Colored lines are generated by a binomial smoother and error bars indicate 95\\% confidence intervals computed by non-parametric bootstrap."}

acc_plot_1a <- ggplot(aes(x=condition_short, y=mean_accuracy), data=ms_rep) + 
    geom_bar(stat = "identity", aes(fill = condition_short)) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   size=0.6,
                   position=position_dodge(width=0.9)) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    facet_grid(.~category_type) +
    coord_cartesian(ylim=c(0.4,1.0)) +
    scale_fill_solarized() +
    ylab("Mean Accuracy") +
    xlab("Condition") +
    facet_grid(.~category_type) +
    theme(text = element_text(size=16)) +
    guides(fill=F) +
    theme_bw()

block_plot_exp1 <- ggplot(aes(x=as.numeric(block), y=mean_accuracy, color = condition_short), 
                          data=filter(ms_rep_block, category_type == "Rule-Based")) +
    binomial_smooth() +
    geom_pointrange(aes(ymin=mean_accuracy - ci_low, 
                        ymax=mean_accuracy + ci_high,
                        color = condition_short), 
                    size=0.3) +
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    facet_grid(.~category_type) +
    scale_y_continuous(limits=c(0.4,1.0)) +
    scale_x_continuous(limits=c(0.5,6.5), breaks = seq(1:6)) +
    scale_color_solarized() +
    ylab("Mean Accuracy") +
    xlab("Block") +
    guides(color = F) +
    theme(text = element_text(size=16)) +
    theme_bw()

block_plot_exp1 <- direct.label(block_plot_exp1, list(last.points, hjust = -0.5))
gridExtra::grid.arrange(acc_plot_1a, block_plot_exp1, ncol = 2, widths = c(2.5,3))
```

## Methods

### Participants

```{r rep1a-demographics}
demographics_replication <- df_rep %>% 
    distinct(subids) %>% 
    xtabs(formula = ~ condition_long + category_type_string) %>% 
    as.data.frame() %>% 
    rename(count = Freq)

dnu_exp1a <- df_rep %>% distinct(subids) %>% count(understand) %>% filter(understand == "No")

n_active_rep_1a <- demographics_replication$count[1]
n_passive_rep_1a <- demographics_replication$count[2]
```

We posted a set of Human Intelligence Tasks (HITs) to Amazon Mechanical Turk. Only participants with US IP addresses and a task approval rate above 85% were allowed to participate, and each HIT paid one dollar. Approximately 25 HITs were posted for each of the two between-subjects conditions. Data were excluded if participants completed the task more than once or if they reported that they did not understand the task at the end of the experiment (`r dnu_exp1a$n` HITs). The final sample consisted of `r (n_passive_rep_1a + n_active_rep_1a) - dnu_exp1a$n` participants. 


```{r data-filter-1a}
df_rep %<>% filter(understand != "No")
```

### Stimuli

The left panel of Figure 1 shows a screenshot of the stimuli used in Experiments 1a, 1b, and 2. Visual stimuli were black "antennas" on a white background. Each antenna could vary along two continuous dimensions -- radius size or central angle -- and was assigned a value between 1 and 600. These values were converted to pixel values for display on a computer screen. To ensure that participants could not complete a full rotation of the antenna, the rotation of the central angle was limited to 150 degrees. The minimum radius and angle values were randomized for each participant, such that each participant was assigned a unique optimal decision boundary. Finally, we used a Rule-Based category structure where the category boundary is defined along a single dimension: either the antenna's size or central angle  (see right panel of Figure 1). 

Radius and angle values for the 96 passive training trials were generated from two Gaussian distributions with identical mean and covariance parameters as @markant2014better (see the right panel of Figure 1). For test trials, we created a uniform grid of 192 unique test items that covered the entire feature space. We randomly sampled 8 items from each quadrant to get 32 test trials for each block. We then randomized the order of the training and test trials within each block for each participant. 

### Design and procedure

Participants saw a total of 288 trials (96 training trials and 192 test trials) across 6 blocks. Each block consisted of 16 training trials and 32 test trials. Before starting the task, participants were told that this was a game where they would see "loop antennas" for televisions and each antenna received one of two channels (CH1 or CH2), and their goal was to learn the difference between the two types of antennas. We introduced some uncertainty by telling participants that the antennas could pick up the wrong channel on occasion, and that they should learn what channel is most often received by a particular type of antenna.

After the instructions, participants were randomly assigned to one the two between-subjects conditions (Active vs. Passive training). In the Active training condition, participants were able to design their own antennas to test. They modified the antenna by clicking and dragging the mouse from left to right. To change the size of the antenna, they first pressed the "Z" key. To change the angle, they first pressed the "X" key. When participants were finished with their design, they pressed the spacebar to see which channel (Ch1 or Ch2) the antenna received. The channel label appeared in a text box with a green border located above the antenna.

In the Passive training condition, participants were shown antennas with size and angles generated from the underlying category distributions. After a two second delay they were told which channel the antenna received. To ensure that participants saw the channel, they had to click on the channel text in order to advance the experiment. When they clicked the channel text, a green box appeared around the text to indicate that their response had been recorded.

After completing the training, participants in both conditions proceeded to the test trials. On each test trial participants saw an antenna and were asked, "Which channel does this antenna receive?" To indicate their response participants selected one of two buttons located above the antenna. 

## Results and Discussion

### Overall classification accuracy

First, we directly follow the analysis plan of @markant2014better, using a t-test to directly compare overall test performance for participants in the active and passive learning conditions. All of our data, processing, and analysis code can be viewed in the version control repository for this paper at: `https://github.com/kemacdonald/act-learn`. The left panel of Figure 2 shows overall test performance, with active learners being more accurate than passive learners, $t$(`r rep1a_t_test$parameter`) = `r round(rep1a_t_test$statistic, 2)`, $p$ = `r round(rep1a_t_test$p.value, 3)`. 

### Classification accuracy across blocks

```{r}
mix_model_exp1a <- glmer(correct ~ condition * block + (1|subids), 
            data=filter(df_rep,trial_type=="test"), family=binomial) 
```

The right panel of Figure 2 shows participants' accuracies across blocks in the experiment. To quantify participants' behavior, we use mixed effects regression models with the maximal random effects structure justified by our experimental design: by-subject intercepts. All mixed-effects models were fit using the lme4 package in R [@bates2013lme4]. We fit a logistic regression predicting test performance based on condition (active/passive) and block. The model was specified as \texttt{Correct $\sim$ 1 + Condition * Block + (1 | subject)}. We found a significant main effect of condition ($\beta$ = `r round(summary(mix_model_exp1a)$coef[2], 2)`, p < .001) with better performance for active learners, and significant main effect of block ($\beta$ = `r round(summary(mix_model_exp1a)$coef[3], 2)`, p < .001) such that responses were more accurate as the number of blocks increased.

### Relationship between sampling behavior and learning

```{r sampling-data}
df_rep_all <- df %>% filter(condition =="AA", category_type == "Rule-Based")
df_sampling_exp1 <- df %>% filter(condition == "AA", category_type == "Rule-Based", trial_type == "training")
```

```{r avg_samp_dist_trials}
df_sampling_exp1 <- mutate(df_sampling_exp1, 
                      samp_dist_odb = ifelse(odb_scale == "orientation" & category_type == "Rule-Based", 
                                             abs(as.numeric(odb_param) - orientation_response_param),
                                             ifelse(odb_scale == "radius" & category_type == "Rule-Based", 
                                                    abs(as.numeric(odb_param) - radius_response_param),
                                                    abs(orientation_response_param - radius_response_param))))
```

```{r avg_samp_dist_subs}
ss_samp_dist_exp1 <- df_sampling_exp1 %>%
    filter(trial_training_block == "active") %>%
    group_by(subids, condition, block, category_type, experiment) %>%
    summarise(mean_samp_dist = mean(samp_dist_odb),
              ci_high_msd = ci.high(samp_dist_odb),
              ci_low_msd = ci.low(samp_dist_odb))

ss_mean_acc_active_block_exp1 <- df_rep_all %>%
    filter(trial_training_block == "active", trial_type == "test") %>%
    group_by(subids, condition, block, category_type, experiment) %>%
    summarise(mean_accuracy_active_block = mean(correct),
              ci_high_acc_active_block = ci.high(correct),
              ci_low_acc_active_block = ci.low(correct))

ss_mean_acc_all_exp1 <- df_rep_all %>%
    filter(trial_type == "test") %>%
    group_by(subids, condition, category_type, experiment) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high_acc = ci.high(correct),
              ci_low_acc = ci.low(correct))

# join sampling and test acc together
ss_all_exp1 <- left_join(ss_samp_dist_exp1, ss_mean_acc_active_block_exp1, 
                         by=c("subids", "condition", "block", "category_type", "experiment"))

ss_all_exp1 <- left_join(ss_all_exp1, ss_mean_acc_all_exp1, 
                         by=c("subids", "condition", "category_type", "experiment"))
```

```{r exp1a_sampling_mixed_model}
lmodel_samp_exp1a <- lm(mean_accuracy ~ mean_samp_dist, 
                             data=filter(ss_all_exp1, experiment == "replication_1a"))
```

We were also interested in the relationship between participants' overall sampling behavior and learning outcomes. We follow &markant2014better and quantify the quality of a sample based on it's orthogonal distance from the true category boundary, with samples closer to the boundary being of higher quality. For each participant, we computed a mean accuracy score and a mean sample distance score, and fit a linear model using sample distance to predict accuracy. We found a signficant effect of sample distance ($\beta$ = -.0003, p < .001) with accuracy increasing as mean sample distance decreased. 

Taken together, our data provide strong evidence for a successful replication of the original results reported in @markant2014better. We found a comparable advantage in overall classification accuracy for active learners over receptive learners in a web-based experiment with two fewer training/test trial blocks. Our results differ from the original study in that we found an immediate advantage for active learners after the first block that was not present in the original study. Next we attempt to replicate @markant2014better's findings for the II category structure and for the yoked passive learning condition.

# Experiment 1b

The goals of Experiment 1b are to (a) replicate @markant2014better's findings for the more difficult II category structure, and (b) replicate their finding that passive learners did not benefit from being "yoked" to active learner's data.\footnote{Yoked designs are important because they help dissociate the effects of selection from the effects of seeing better data.} They did not find an active learning advantage for the II category structure and yoked learners were worse than active learners even though they had seen the exact same learning information. We used the same stimuli and followed the exact procedures as the original study (described below). However, we reduced the length of the experiment to two blocks. We made this decision based on finding an immediate active learning advantage in Experiment 1a.

```{r rep1b-data}
df_rep1b <- df %>% 
    filter(experiment == "replication_1b", 
           condition_short %in% c("A","R","Y")) 
```

## Methods

### Stimuli
Visual stimuli were identical to Experiment 1a. We use both the RB category from Experiment 1a, and we add the II category. The II category boundary is defined by a linear combination of the size and angle dimensions (see right panel of Figure 1). 

### Participants

```{r rep1b-participants}
demographics_replication_1b <- df_rep1b %>% 
    distinct(subids) %>% 
    xtabs(formula = ~ condition_long + category_type_string) %>% 
    as.data.frame() %>% 
    rename(count = Freq)

dnu_exp1b <- df_rep1b %>% distinct(subids) %>% count(understand) %>% filter(understand == "No")

# get num subs in each condition
nsubs_active_ii_rep_1b <- demographics_replication_1b$count[1]
nsubs_passive_ii_rep_1b <- demographics_replication_1b$count[2]
nsubs_yoked_ii_rep_1b <- demographics_replication_1b$count[3]

nsubs_active_rb_rep_1b <- demographics_replication_1b$count[4]
nsubs_passive_rb_rep_1b <- demographics_replication_1b$count[5]
nsubs_yoked_rb_rep_1b <- demographics_replication_1b$count[6]
```

Participant recruitment and inclusionary/exclusionary criteria were identical to those of Experiment 1a (excluded `r dnu_exp1b` HITs). `r sum(demographics_replication_1b$count)` HITs were posted across each of the category structures (II and RB) and training conditions (Active, Passive, and Yoked).

```{r data-filter-1b}
df_rep1b %<>% filter(understand != "No")
```

### Design and procedure

Procedures were identical to those of Experiment 1a. We added a "yoked" learning condition, in which we match each passive learning participant with training data generated from an active learning participant's sampling behavior. Thus, both the active and yoked participants saw the exact same data, but the active participants were in control of the information flow.

## Results and Discussion

```{r rep1b-mean-acc}
ms_rep_1b <- df_rep1b %>%
    filter(trial_type == "test") %>%
    group_by(condition_short, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

```{r rep1b-acc-plot, fig.env = "figure", fig.pos = "t", fig.width=3, fig.height=2.8, fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "The left panel shows overall accuracy performance for the Active and Passive training conditions. The right panel shows participants' accuracy across all six blocks in the experiment."}

ggplot(aes(x=condition_short, y=mean_accuracy), data=ms_rep_1b) + 
    geom_bar(stat = "identity", aes(fill = condition_short)) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   size=0.6,
                   position=position_dodge(width=0.9)) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    facet_grid(.~category_type) +
    coord_cartesian(ylim=c(0.4,1.0)) +
    scale_fill_solarized() +
    ylab("Mean Accuracy") +
    xlab("Condition") +
    facet_grid(.~category_type) +
    theme(text = element_text(size=16)) +
    guides(fill=F) +
    theme_bw()

```

### Relationship between sampling and test across blocks

```{r exp1_sampling-acc-plot, fig.env = "figure", fig.pos = "h", fig.width=3.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "The relations between quality of sampling and accuracy on test trials across blocks."}

ggplot(aes(x=mean_samp_dist, y=mean_accuracy_active_block), 
                 data = filter(ss_all_exp1, block %in% c(1, 2))) +
    geom_point() +
    geom_smooth(method="lm") +
    facet_grid(.~block) +
    xlab("Mean Sample Distance") +
    ylab("Mean Accuracy") +
    theme(text = element_text(size=16)) +
    theme_bw()

```

# Experiment 2

```{r seq-data}
df_sequence <- df %>% filter(block == 1 | block == 2,
                             experiment == "sequence",
                             condition %in% c("RA", "AR"))

df_sequence_rep <- df %>% filter(block == 1 | block == 2,
                             condition %in% c("RA", "AR", "RR", "AA"))
```

## Methods

### Stimuli
Stimuli were identical to Experiment 1.  

### Participants

```{r seq-participants}
demographics_sequence <- df_sequence %>% 
    distinct(subids) %>% 
    xtabs(formula = ~ condition_long + category_type_string) %>% 
    as.data.frame() %>% 
    rename(count = Freq)

dnu_sequence <- df_sequence %>% distinct(subids) %>% 
    count(understand) %>% 
    filter(understand == "No")

# get num subs in each condition
nsubs_ar_ii <- demographics_sequence$count[1]
nsubs_ra_ii <- demographics_sequence$count[2]

nsubs_ar_rb <- demographics_sequence$count[3]
nsubs_ra_rb <- demographics_sequence$count[4]
```

Participant recruitment and inclusionary/exclusionary criteria were identical to those of Experiment 1 (`r dnu_sequence` HITs). Approximately 44 HITs were posted for each condition for total of `r sum(demographics_sequence$count)` paid HITs.

```{r}
df_sequence <- df_sequence %>% filter(understand != "No")
df_sequence_rep <- df_sequence_rep %>% filter(understand != "No")
```

### Design and procedure

## Results and Discussion

```{r seq-acc-computation}
# overall acc
ms_sequence_all <- df_sequence_rep %>%
    filter(trial_type == "test") %>%
    group_by(condition, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))

ms_sequence_block <- df_sequence %>%
    filter(trial_type == "test") %>%
    group_by(condition, block, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

```{r exp2_acc_plot, fig.env = "figure*", fig.pos = "h", fig.width=5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows accuracy performance across both blocks for the different sequence of active/passive training. The right panel shows overall accuracy performance plotted with the active-active and receptive-receptive data from Experiment 1."}

acc_plot_seq <- ggplot(aes(x=condition, y=mean_accuracy), data=ms_sequence_all) + 
    geom_bar(stat = "identity", aes(fill = condition)) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   size=0.6,
                   position=position_dodge(width=0.9)) + 
    facet_grid(.~category_type) +
    coord_cartesian(ylim=c(0.5,0.9)) +
    scale_fill_solarized() +
    ylab("Mean Accuracy") +
    xlab("Condition") +
    theme(text = element_text(size=16)) +
    guides(fill=F) +
    theme_bw()


block_plot_seq <- ggplot(aes(x=block, y=mean_accuracy), data=ms_sequence_block) +
    geom_pointrange(aes(ymin=mean_accuracy - ci_low, 
                        ymax=mean_accuracy + ci_high,
                        color = condition), 
                    size=0.6) +
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    geom_smooth(aes(color = condition), method = "lm", se=F) +
    facet_grid(.~category_type) +
    scale_x_discrete() +
    scale_y_continuous(limits=c(0.5,0.9)) +
    scale_color_solarized() +
    ylab("Mean Accuracy") +
    xlab("Block") +
    guides(color = F) +
    theme(text = element_text(size=16)) +
    theme_bw()

block_plot_seq <- direct.label(block_plot_seq, list(last.bumpup, hjust = -0.5))
block_plot_seq
```

# Experiment 3

Experiment 3 is a conceptual replication of the order effect findings using a novel paradigm where participants learn a higher dimensional concept.

## Methods

### Stimuli

### Participants
Participant recruitment, and inclusionary/exclusionary criteria were identical to those of Experiment 1 and 2 (excluded TODO HITs). 40 HITs were posted for each condition (TODO) for total of TODO paid HITs.  

### Design and procedure

## Results and Discussion

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)
tab <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2))
print(tab, type="latex", comment = F, table.placement = "H")
```

# General Discussion

* Recap findings
    * Active learning advantage in a direct replication (yay science!)
    * Passive-active better than Active-passive
    * Conceptual replication
    
* Expand on why we see AR > RA
    * Sequential hypothesis testing model 
    * Gain some understanding of task before exploring
    * RA is bad because you can't refine your current hypothesis. Can only use the data you are given
    to confirm/reject current hypothesis

* Limitations
    * AA was always best
    * task analysis 
    * complexity of real world learning
    
* Takeaway point: 

# Acknowledgements

We are grateful to Doug Markant and Todd Gureckis for sharing the details and code from the original experiment. We thank the members of the Language and Cognition Lab for their helpful feedback on this project. This work was supported by a National Science Foundation Graduate Research Fellowship to KM.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
