s---
title: "Active Learning Parameter Values"
author: "Kyle MacDonald"
date: "July 21, 2015"
output: html_document
---

This script generates parameter values for active category learning experiment.

Set seed so we can recreate our sampling procedures.

```{r}
set.seed(seed = 43)
```

Load packages

```{r}
library(rjson)
library(gridExtra)
library(ggplot2)
library(MASS)
library(dplyr)
theme_set(theme_bw())
```

## Experiment information 

```{r}
n_blocks <- 2
n_trials_in_block <- 16
n_trials <- n_blocks * n_trials_in_block
n_trials_cat <- n_trials / 2
test_trials_block <- 32
n_test_trials <- n_blocks * test_trials_block
n_trials_quadrant <- test_trials_block / 4
```

## Rule-Based Condition 

### Training Trials

Category A1

```{r}
a1.rad.mean <- 220
a1.rad.sd <- sqrt(2000)
a1.orientation.mean <- 300
a1.orientation.sd <- sqrt(9000)
a1_radii <- floor(rnorm(n_trials_cat, mean = a1.rad.mean, sd = a1.rad.sd))
a1_orientations <- floor(rnorm(n_trials_cat, mean = a1.orientation.mean, sd = a1.orientation.sd))
```

Category B1

```{r}
b1.rad.mean <- 380
b1.rad.sd <- sqrt(2000)
b1.orientation.mean <- 300
b1.orientation.sd <- sqrt(9000)
b1_radii <- floor(rnorm(n_trials_cat, mean = b1.rad.mean, sd = b1.rad.sd))
b1_orientations <- floor(rnorm(n_trials_cat, mean = b1.orientation.mean, sd = b1.orientation.sd))
```

Convert to json 

```{r, eval=FALSE}
toJSON(a1_radii)
toJSON(a1_orientations)
toJSON(b1_radii)
toJSON(b1_orientations)
```

Create data frame

```{r}
df <- data.frame(orientation = a1_orientations, radii = a1_radii, category = "a", 
                 condition = "1") %>% 
    bind_rows(data.frame(orientation = b1_orientations, radii = b1_radii, category = "b",
                         condition = "1"))
```

### Category A2

```{r}
a2.rad.mean <- 300
a2.rad.sd <- sqrt(9000)
a2.orientation.mean <- 220
a2.orientation.sd <- sqrt(2000)
a2_radii <- floor(rnorm(n_trials_cat, mean = a2.rad.mean, sd = a2.rad.sd))
a2_orientations <- floor(rnorm(n_trials_cat, mean = a2.orientation.mean, sd = a2.orientation.sd))
```

### Category B2

```{r}
b2.rad.mean <- 300
b2.rad.sd <- sqrt(9000)
b2.orientation.mean <- 380
b2.orientation.sd <- sqrt(2000)
b2_radii <- floor(rnorm(n_trials_cat, mean = b2.rad.mean, sd = b2.rad.sd))
b2_orientations <- floor(rnorm(n_trials_cat, mean = b2.orientation.mean, sd = b2.orientation.sd))
```

### Convert to json 

```{r, eval=FALSE}
toJSON(a2_radii)
toJSON(a2_orientations)
toJSON(b2_radii)
toJSON(b2_orientations)
```

### Plot 

```{r, fig.width=8, fig.height=4}
df_2 <- data.frame(orientation = a2_orientations, radii = a2_radii, category = "a",
                   condition = "2") %>% 
    bind_rows(data.frame(orientation = b2_orientations, radii = b2_radii, category = "b", 
                         condition = "2"))

df_final <- bind_rows(df, df_2)
```

```{r}
df_abline1 <- data.frame(condition = c("1", "2"), y_intercept = c(-10, 300), x_intercept = c(300, -10))

plot1 <- qplot(radii, orientation, color = category, data=df_final, size = 1,
               facets = condition ~ ., xlim=c(0,600), ylim=c(0,600)) + 
    geom_hline(data=df_abline1, aes(yintercept = y_intercept), color = "blue", size = 1) +
    geom_vline(data=df_abline1, aes(xintercept = x_intercept), color = "blue", size = 1) +
    guides(size = F, color = F)

plot1
```

## Information Integration Condition 

Next we generate values for the information integration condition. This is
very similar to the Rule-based categories, with the main difference being
that there is covariance between the angle and radius values. In this condition, 
the optimal classification rule is a linear combination of the values along two dimensions.

### Category A1

```{r}
var_radii <- 4538
var_orientations <- 4538
cov_ro <- 4463
Sigma <- matrix(c(var_radii, cov_ro, cov_ro, var_orientations),2,2)
df <- data.frame(floor(mvrnorm(n = n_trials_cat, mu = c(250, 350), Sigma, empirical = T)))
df$category <- "a"
df$condition <- "1"
```

### Category B1

```{r}
var_radii <- 4538
var_orientations <- 4538
cov <- 4463
Sigma <- matrix(c(var_radii, cov_ro, cov_ro, var_orientations),2,2)
df_2 <- data.frame(floor(mvrnorm(n = n_trials_cat, mu = c(350, 250), Sigma, empirical = T)))
df_2$category <- "b"
df_2$condition <- "1"
```

### Category A2

```{r}
var_radii <- 4538
var_orientations <- 4538
cov_ro <- -4463
Sigma <- matrix(c(var_radii, cov_ro, cov_ro, var_orientations),2,2)
df_3 <- data.frame(floor(mvrnorm(n = n_trials_cat, mu = c(250, 250), Sigma, empirical = T)))
df_3$category <- "a"
df_3$condition <- "2"
```

### Category B2

```{r}
var_radii <- 4538
var_orientations <- 4538
cov_ro <- -4463
Sigma <- matrix(c(var_radii, cov_ro, cov_ro, var_orientations),2,2)
df_4 <- data.frame(floor(mvrnorm(n = n_trials_cat, mu = c(350, 350), Sigma, empirical = T)))
df_4$category <- "b"
df_4$condition <- "2"
```

### Plot

```{r}
# create data frame 
df_final2 <- rbind(df, df_2, df_3, df_4)
names(df_final2) <- c("radii", "orientation", "category", "condition")
```

```{r}
df_abline <- data.frame(condition = c("1", "2"), intercept = c(0, 600), slope = c(1, -1))

plot2 <- qplot(radii, orientation, data = df_final2, color = category, size = 1,
               facets = condition ~ .) +
    xlim(0, 600) +
    ylim(0, 600) +
    geom_abline(data = df_abline, aes(intercept=intercept, slope=slope), 
                color = "blue", size = 1) +
    guides(size = F)
    
plot2
```

Helper function to compute the perendicular distance from a point to a line

```{r}
perp_dist_function <- function(x, y, a, b, c) {
    distance <- (a*x + b*y + c) / (sqrt(a^2 + b^2))
    distance
}

perp_dist_function(x = 300, y = 300, a = -1, b = -1, c = 600) # positive value, below the line
perp_dist_function(x = 300, y = 300, a = -1, b = 1, c = 0) # positive value, above the line
```

Show parameter values for all conditions and categories.

```{r, fig.height=6}
grid.arrange(plot1, plot2, ncol = 2)
```

### Convert to JSON

```{r}
# Order 1
toJSON(df$X1) # A1 radii
toJSON(df$X2) # A1 angles
toJSON(df_2$X1) # B1 radii
toJSON(df_2$X2) # B1 angles

# Order 2
toJSON(df_3$X1) # A2 radii
toJSON(df_3$X2) # A2 angles
toJSON(df_4$X1) # B2 radii
toJSON(df_4$X2) # B2 angles
```

## Test trials

Algorithm for generating test trials:
*uniform grid across parameter space
*randomly sample from each quadrant such that
*each block has 8 trials from each
*then shuffle those blocks

### Make quadrants in parameter space 

```{r}
quad1.x <- seq(1,300)
quad1.y <- seq(301,600)
quad2.x <- seq(301,600)
quad2.y <- seq(301,600)
quad3.x <- seq(1,300)
quad3.y <- seq(1, 300)
quad4.x <- seq(301,600)
quad4.y <- seq(1,300)
```

Function that samples from each of these quadrants

```{r}
# no inputs
# returns an array of radii and orientation values, 
# 8 from each quadrant, in parameter space
rand.quad <- function(n_blocks, n_trials_quadrant) {
    radius.vals <- vector()
    orientation.vals <- vector()
    for (i in 1:n_blocks) {
        for (j in 1:n_trials_quadrant) {
            radius.vals <- c(radius.vals, sample(quad1.x, 1))
            radius.vals <- c(radius.vals, sample(quad2.x, 1))
            radius.vals <- c(radius.vals, sample(quad3.x, 1))
            radius.vals <- c(radius.vals, sample(quad4.x, 1))
            orientation.vals <- c(orientation.vals, sample(quad1.y, 1))
            orientation.vals <- c(orientation.vals, sample(quad2.y, 1))
            orientation.vals <- c(orientation.vals, sample(quad3.y, 1))
            orientation.vals <- c(orientation.vals, sample(quad4.y, 1))
        }
    }
    list.vals <- list("radii" = radius.vals, "angles" = orientation.vals)
    
    return(list.vals)
}
```

Get values for test trials using the new function.

```{r}
test.trials.vals <- rand.quad(n_blocks, n_trials_quadrant) 
```

Plot test trial values to make sure we have a relatively uniform 
distribution across potential parameter values.

```{r}
qplot(test.trials.vals$radii, test.trials.vals$angles) +
    geom_hline(y = 300, color = "blue") +
    geom_line(x = 300, color = "blue") + 
    geom_abline(intercept = 0, slope = 1) +
    geom_abline(intercept = 600, slope = -1)
```

### Convert to JSON

```{r, eval=FALSE}
toJSON(test.trials.vals)
```
