---
title: "act-learn-power"
author: "Kyle MacDonald"
date: "July 28, 2015"
output: html_document
---

# Power Analysis

For Markant and Gureckis, 2014 active learning vs. passive learning t.test.


```{r}
rm(list=ls())
library(compute.es)
library(pwr)
```

## Post hoc power Markant and Gureckis, 2014 

```{r}
t.val <- 1.82
n.1 <- 30
n.2 <- 30
es <- tes(t.val, n.1, n.2)
cohens.d <- es$d
```

### Effect size from MacDonald, 2015 replication 

```{r}
t.val.km <- 2.3683
n.1.km <- 24
n.2.km <- 23
es.km <- tes(t.val.km, n.1.km, n.2.km)
cohens.d.km <- es.km$d
```

### A priori power analysis for full replication experiment

```{r}
pwr.t.test(d=cohens.d.km,power=0.8,sig.level=0.05,type="two.sample",alternative="greater")
```

### Act-learn Sequence Power

First, we get the effect size for the mean difference between AR and RA groups.

```{r}
t.val.seq <- -1.5475
n.1.seq <- 29
n.2.seq <- 23
es.seq <- tes(t.val.seq, n.1.seq, n.2.seq)
d.seq <- es.seq$d
```

Next, we compute an a priori power analysis to detect this effect

```{r}
pwr.t.test(d = d.seq, power = 0.8, sig.level = 0.05, type = "two.sample", alternative = "two.sided")
```