---
title: "Act-Learn Yoked Parameters"
author: "Kyle MacDonald"
date: "October 6, 2015"
output: html_document
---

Set seed

```{r}
rm(list=ls())
set.seed(5)
```

Load packages

```{r}
library(rjson)
library(jsonlite)
library(stringr)
library(dplyr)
library(magrittr)
```

## Yoked Learning Data

Load active learners' sampling data

```{r}
df <- read.csv("../../data/act-learn-ii-rb-replication.csv")

df %<>% 
    filter(trial_type == "training", condition == "active") %>% 
    select(subids, category_type, order, radius_response_param, orientation_response_param, 
           trial_category, orientation_response_stim, radius_response_stim)
```

### Sample active learners data

Need to get 56 participants, with 14 from each category (rb/ii) and order combination (1/2).

```{r}
df_subs <- df %>% 
    group_by(subids, category_type) %>% 
    distinct() %>% 
    select(subids, category_type, order) %>% 
    group_by(category_type)

df_subs %>% group_by(category_type, order) %>% summarise(n())
```

```{r}
subs <- sample_n(df_subs, size = 27, replace = F) %>% 
    select(subids, order) %>% 
    mutate(use_in_yoked = "yes")
```

```{r}
subs %>% group_by(category_type, order) %>% summarise(n())
```

```{r}
df <- left_join(df, subs, by = c("subids", "category_type", "order")) 
df %<>% mutate(use_in_yoked = ifelse(is.na(use_in_yoked), "no", use_in_yoked))
```

Grab radius and orientation parameters for these participants.

```{r}
df_in_yoked <- filter(df, use_in_yoked == "yes")
```

```{r}
grab_antenna_params <- function(df) {
    radius.vals <- df$radius_response_param
    orientation.vals <- df$orientation_response_param
    radius.vals.stim <- df$radius_response_stim
    orientation.vals.stim <- df$orientation_response_stim
    category.vals <- df$trial_category
    
    list.vals <- list("radii" = radius.vals, "angles" = orientation.vals, 
                      "radii_stim" = radius.vals.stim, "angles_stim" = orientation.vals.stim, 
                      "category" = category.vals)
    
    return(list.vals)
}

df_final <- df_in_yoked %>% 
    group_by(subids, category_type, order) %>% 
    do(antenna_vals = data.frame(grab_antenna_params(.))) 
    
cond_indicator <- 1:nrow(df_final)

df_final <- cbind(cond_indicator, df_final)
```

### Convert to JSON object

Use jsonlite to convert data frame to JSON object to play nice with javascript.

```{r}
jsonlite::toJSON(df_final, complex = "string", pretty = F)
```

This is better because we don't have to do string replacement. yay!