---
title: "Act-Learn Rule-Based Category Analysis"
author: "Kyle MacDonald"
date: "September 30, 2015"
output: html_document
---

This script analyzes data from a replication experiment testing the effectiveness of active
vs. passive training in a category learning task. 

## Libraries 

```{r libraries, warning=F, message=F, comment=F}
rm(list=ls())
source("helpers/useful.R")
library(langcog)
library(dplyr)
library(magrittr)
```

## Load data

```{r load data}
df <- read.csv("../data/act-learn-rb-original-replication.csv", stringsAsFactors = F)
```

## Grab just the first two blocks

So we can analyze with the extension experiments, which only ran 2 blocks.

```{r, eval=F}
df_2blocks <- filter(df, block == 1 | block == 2)
write.csv(df_2blocks, "../data/act-learn-replication-first2-blocks.csv")
```

## Exclusionary criteria

Overall performance (averaged across blocks) was more than three standard deviations below the mean of their group.

```{r exclusionary}
ss <- df %>%
    filter(trial_type == "test") %>%
    group_by(subids, condition) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high_acc = ci.high(correct),
              ci_low_acc = ci.low(correct))

# get the mean and standard deviation of each group
ms_ss <- ss %>%
    group_by(condition) %>%
    summarise(group_mean = mean(mean_accuracy),
              group_sd = sd(mean_accuracy))
```

Map means and sd to variables

```{r}
# active rb
mean_act_rb <- filter(ms_ss, condition == "active")$group_mean
sd_act_rb <- filter(ms_ss, condition == "active")$group_sd


# receptive rb
mean_rec_rb <- filter(ms_ss, condition == "receptive")$group_mean
sd_rec_rb <- filter(ms_ss, condition == "receptive")$group_sd

```

Flag subject means that are +/- 3sd 

```{r}
ss_include <- ss %>%
    mutate(
        include = ifelse(condition == "active", 
                         ifelse(mean_accuracy > mean_act_rb + 3 * sd_act_rb | 
                                    mean_accuracy < mean_act_rb - 3 * sd_act_rb, "remove", "include"),
                         ifelse(mean_accuracy > mean_rec_rb + 3 * sd_rec_rb | 
                                    mean_accuracy < mean_rec_rb - 3 * sd_rec_rb, "remove", "include"))) %>% 
    select(subids, include, condition) 

ss_include %>%
    group_by(condition, include) %>%
    summarise(n())

# merge with full data frame
df <- left_join(df, select(ss_include, subids, include, condition), by = c("subids", "condition"))

# filter out subjects that are +/- 3sd
df <- df %>% filter(include == "include")
```

## Remove participants how didn't understand the task

```{r}
df %<>% filter(understand == "Yes")
```

## Descriptives

```{r demographics, echo=FALSE}
demo_df <- df %>% 
    distinct(subids) %>% 
    xtabs(formula = ~ condition  + order) %>% 
    as.data.frame() %>% 
    rename(count = Freq)

demo_df <- df %>% 
    group_by(subids, condition, order) %>%
    summarise(exp_length_minutes = sum(rt) / 60000) %>% 
    group_by(condition) %>% 
    summarise(mean_exp_length = mean(exp_length_minutes)) %>% 
    left_join(demo_df, by = c("condition"))
    
knitr::kable(demo_df)
```

## Descriptives

Histogram of length of experiment split by condition 

```{r, echo=F}
ss_rt <- df %>%
    group_by(subids, condition) %>%
    summarise(exp_length_min = sum(rt) / 60000)

qplot(exp_length_min, data=ss_rt, facets=.~condition)
```

## Overall accuracy analysis 

Get mean accuracy for each condition and category type

```{r, echo=F}
ms <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot.

```{r mean acc plot condition/order, echo=F}
qplot(x=condition, y=mean_accuracy, data=ms,
      geom="bar", stat="identity", fill = condition, position = "dodge") + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6, position=position_dodge(width=0.9)) + 
    scale_fill_brewer(type = "qual", palette = "Set1") +
    coord_cartesian(ylim=c(0.5,1)) +
    theme_classic() +
    ylab("Mean Accuracy") +
    xlab("Condition") +
    theme_classic() +
    theme(text = element_text(size=16))
```

## Accuracy by block analysis

```{r acc by block, echo=F}
ms_block <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, block) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot accuracy over blocks

```{r acc by block plot, echo=F}
qplot(x=block, y=mean_accuracy, data=ms_block, color = condition,
      geom=c("blank"), stat="identity") +
    geom_smooth(method = "lm", se=F) +
    geom_pointrange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6) + 
    scale_x_discrete() +
    scale_y_continuous(limits=c(0.5,1)) +
    scale_color_brewer(type = "qual", palette = "Set1") +
    ylab("Mean Accuracy") +
    xlab("Block") +
    theme_bw() +
    theme(text = element_text(size=16))
```

Accuracy by block and dimension.

```{r acc by block and dimension, echo=F}
ms_block <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, block_factor, order) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot accuracy over blocks

```{r acc by block and dim plot, echo=F}
qplot(x=block_factor, y=mean_accuracy, data=ms_block, color = condition,
      geom=c("point", "line"), stat="identity", facets=~order) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6) + 
    scale_color_brewer(type = "qual", palette = "Set1") +
    scale_y_continuous(limits=c(0,1)) +
    scale_x_discrete() +
    ylab("Mean Accuracy") +
    xlab("Block") +
    theme_bw() +
    theme(text = element_text(size=16))
```

## Evidence selection analysis (active learning)

Analyze the average distance of participants' samples from the optimal decision
boundary.

```{r sampling data, echo=F}
df %<>% mutate(trial_training_block = ifelse(condition == "active_receptive" & block == 1, "active",
                                             ifelse(condition == "receptive_active" & block == 2,
                                             "active", "receptive")))


df_sampling <- df %>% filter(trial_type == "training", trial_training_block == "active")
```

Rotate, so orientation and radius are on the same dimension.

* dim of interest = dimension with category boundary
* other dim = dimesnion that does not contain the category boundary 

```{r rotate samples, echo=F}
df_sampling <- df_sampling %>%
    mutate(dim_of_interest = ifelse(odb_scale == "orientation_scale" & condition == "rule-based",
                                    orientation_response_param,
                                    radius_response_param),
           other_dim = ifelse(odb_scale == "orientation_scale" & condition == "rule-based",
                              radius_response_param,
                              orientation_response_param))
```

Plot group level sampling behavior.

```{r sampling plot, fig.width=8}
qplot(x=dim_of_interest, y=other_dim, data = df_sampling,
      facets=.~condition, color = trial_response) +
    scale_color_brewer(type = "qual", palette = "Set1") +
    geom_vline(xintercept = 300, color = "blue")
```

Plot individual participant sampling behavior

```{r sampling subs, echo=F, fig.width=10}
qplot(x=dim_of_interest, y=other_dim, data=df_sampling,
      color = block_factor) +
    facet_wrap(~subids) +
    geom_vline(aes(xintercept=300)) 
```

Get distance from optimal decision boundary for each sample.

```{r}
df_sampling <- mutate(df_sampling, 
                      samp_dist_odb = ifelse(odb_scale == "orientation_scale",
                                             abs(odb_param - orientation_response_param),
                                             abs(odb_param - radius_response_param)))
```

Now get the average distance across subjects

```{r}
ms_sampling <- df_sampling %>%
    group_by(condition) %>%
    summarize(mean_samp_dist = mean(samp_dist_odb),
              ci_high = ci.high(samp_dist_odb),
              ci_low = ci.low(samp_dist_odb))
```

Now plot.

```{r}
qplot(x=condition, y=mean_samp_dist, data=ms_sampling, 
      geom="line", ylim=c(75,225)) +
    geom_pointrange(aes(ymin=mean_samp_dist - ci_low, 
                        ymax=mean_samp_dist + ci_high), 
                    width = .05, size=0.6) +
    scale_color_grey() +
    xlab("Block") +
    ylab("Mean Sample Distance") +
    theme(text = element_text(size=16))
```

Compute average response times across blocks 
for the two different dimensions.  

```{r rt over blocks}
ms_rt <- df_sampling %>%
    group_by(block) %>%
    summarise(mean_rt = mean(rt),
              ci_high = ci.high(rt),
              ci_low = ci.low(rt))
```

Now plot.

```{r}
qplot(x=block, y=mean_rt, data=ms_rt, 
      geom="line") +
    geom_pointrange(aes(ymin=mean_rt - ci_low, 
                        ymax=mean_rt + ci_high), 
                    width = .05, size=0.6) +
    scale_color_grey()
```


## Relationship between sampling and test

Sample distance and accuracy

```{r}
ss_samp_dist <- df_sampling %>%
    filter(trial_training_block == "active") %>%
    group_by(subids, condition) %>%
    summarise(mean_samp_dist = mean(samp_dist_odb),
              ci_high_msd = ci.high(samp_dist_odb),
              ci_low_msd = ci.low(samp_dist_odb))

ss_mean_acc <- df %>%
    filter(trial_training_block == "active" & trial_type == "test") %>%
    group_by(subids, condition) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high_acc = ci.high(correct),
              ci_low_acc = ci.low(correct))

# join sampling and test acc together
ss_all <- inner_join(ss_samp_dist, ss_mean_acc, by=c("subids", "condition"))
```

Plot

```{r}
qplot(x=mean_samp_dist, y=mean_accuracy, data=ss_all) +
    geom_smooth(method="lm") +
    facet_grid(~condition) +
    xlab("Mean Sample Distance") +
    ylab("Mean Accuracy") +
    theme(text = element_text(size=16))
```

## Relationship between confidence and accuracy

How to plot continuous predictor and binary outcome with lots of data?

```{r}
df %>%
    filter(trial_type == "test") %>%
    mutate(conf_level = cut(confidence, 8)) %>%
    group_by(condition, conf_level) %>%
    summarise(correct = mean(correct)) %>%
    ggplot(aes(x = conf_level, y = correct, col = condition, group = condition)) +
    geom_point() +
    geom_smooth(se=FALSE) + 
    scale_color_brewer(type = "qual", palette = "Set1")  +
    xlab("Binned Confidence Level") +
    ylab("Mean Proportion Correct") +
    theme(text = element_text(size=16))
```

Predict accuracy based on confidence

```{r }
conf_m1 <- glmer(confidence ~ condition  + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 

summary(conf_m1)
```

Less confident in the receptive condition.

```{r}
conf_m2 <- glmer(correct ~ confidence  + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 

summary(conf_m2)
```

Confidence predicts accuracy 


## Statistics 

t.test testing difference in accuracy on test trials between active and receptive learning conditions.

```{r}
t.test(mean_accuracy ~ condition, var.equal=TRUE, data=ss_all)
```

Replicated the slight boost to accuracy in the active learning condition. 

## LMERs

Model the relationship between mean sampling distance on training trials and mean accuracy
on test trials.

```{r}
m1 <- lm(mean_accuracy ~ mean_samp_dist, data=ss_all)
summary(m1)
```

Negative relationship such that those subjects who sampled farther away from the boundary
were less accurate on test.

Next, we try to predict correct based on condition.

```{r}
m2 <- glmer(correct ~ condition * block + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 
summary(m2)
```

Add rt on test trials to the model

```{r}
m3 <- glmer(correct ~ condition + rt + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 
summary(m3)
```

Add block

```{r}
m4 <- glmer(correct ~ condition + rt + block + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 
summary(m4)
```

```{r}
m5 <- glmer(correct ~ condition * odb_scale + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial)
summary(m5)
```

