---
title: "Importing Act-Learn MTurk JSON data"
output: html_document
author: Kyle MacDonald (adapted from Long Ouyang's script)
---

# Libraries

```{r, message=FALSE}
rm(list=ls())
library(jsonlite)
library(plyr)
library(dplyr)
library(lubridate)
```

Set working directory to where you stored raw JSON files.

```{r}
setwd("../../ACT-LEARN-RAW-DATA/data_summary/prior_manipulation_extension/")
setwd("../../ACT-LEARN-RAW-DATA/data_history/extension_2_sequence_ii/production-results/")
```

# Read in all the JSON strings

```{r comment=NA}
read.file <- function(filename) {
  con <- file(filename, "r", blocking = TRUE)
  lines <- paste(readLines(con, warn = FALSE), collapse = "\n")
  close(con)
  lines
}

json.filenames <- list.files()
json.strings <- Map(read.file, json.filenames)
```

# Convert JSON to a R data frame

Merge all the json strings together, as if they are in a big array, and convert it to an R data frame:

```{r comment=NA}
json.superstring <- paste("[",paste(json.strings, collapse = ","),"]")
assignments <- fromJSON( json.superstring )
```

Only keep unique worker IDs.

```{r comment=NA}
assignments <- distinct(assignments, WorkerId)
```

## Build experiment information data frame.

```{r comment=NA}
exp_df <- data.frame(
    workerid = assignments$WorkerId, 
    approval_time = assignments$AutoApprovalTime,
    odb_stim = unlist(assignments$answers$odb_stim),
    odb_param = unlist(assignments$answers$odb_param),
    odb_scale = unlist(assignments$answers$odb_scale),
    screen_width = assignments$answers$screen_width,
    screen_height = assignments$answers$screen_height,
    condition = assignments$answers$condition,
    #framing_condition = assignments$answers$framing_condition,
    order = assignments$answers$order,
    category_type = assignments$answers$category_type,
    browser = assignments$answers$browser
)
```

## Build subject information data frame.

```{r comment=NA}
sub_df <- cbind(workerid = assignments$WorkerId, assignments$answers$subj_data)
```

## Merge subject and experiment info

```{r comment=NA}
sub_exp_df <- left_join(sub_df, exp_df, by="workerid")
```

## data

This is a little more complicated - a list of data frames. Thankfully, the data farmes have the same structure, so to combine them we can just use rbind. However, it would then be difficult to figure out which rows belong to which subjects.

One way we can do this in R is using `Map`, applies a function and an arbitrary number of list/vector arguments (if you don't understand the difference between lists and vectors, you should Google it).

(Note that `Map` always returns a list regardless of its input types. If you want to convert the output of `Map` to a vector, use `unlist`)

Here's how we zip together the subject ids and trial dataframes - we just Map over every id-dataframe pair and cbind them together:

```{r comment=NA}
trial.data <- Map(function(id, subject.trial.data) 
    { cbind(workerid = id, subject.trial.data) },
                  assignments$WorkerId,
                  assignments$answers$data)
```

Now we can rbind the dataframes together and strip the rownames in the resulting data frame to get what we want:

```{r comment=NA}
strip.rownames <- function(x) {
  rownames(x) <- NULL
  x
}

trial.data <- strip.rownames(do.call(rbind, trial.data))
```

## Merge trial level data with subject/experiment level data

```{r comment=NA}
sub_exp_df <- mutate(sub_exp_df, workerid = as.character(workerid))
trial.data <- mutate(trial.data, workerid = as.character(workerid))

df_final <- left_join(sub_exp_df, trial.data, by="workerid")
```


```{r flag extra subs}
# This drops the weirdo T and Z from the turk timestamps and then parses them into seconds time 0 (some UTC standard)
df_final$approval_time <- parse_date_time(
    gsub("[[:alpha:]]"," ", 
         df_final$approval_time),
    "Ymd hms"
)
```

Do some final clean-up:
- Recode variable values from numeric to meaningful text
- Rename column 

```{r comment=NA}
df_final <- df_final %>%
    rename(understand = asses) %>%
    mutate(enjoyment = revalue(enjoyment, c("0" = "Worse Than Average",
                         "1" = "Average",
                         "2" = "Better Than Average")),
           education = revalue(education, c("0" = "Some High School",
                                            "1" = "Graduated High School",
                                            "2" = "Some College",
                                            "3" = "Graduated College",
                                            "4" = "Higher Degree")),
           block_factor = as.factor(block))
```

## Save output 

```{r comment=NA}
write.csv(x = df_final, file = "../../act-learn-sequence-2.csv", row.names=F)
```
