---
title: "Act-Learn Analysis"
author: "Kyle MacDonald"
output: html_document
---

This script analyzes data from an experiment testing the effectiveness of active, passive, and pedagogical training in a category learning task.

```{r}
rm(list=ls())
knitr::opts_chunk$set(warning=FALSE, message=FALSE, sanitize = T, 
                      fig.height=6, fig.width=9, echo=F, cache = T)

```

## Libraries 

```{r libraries, warning=F, message=F, comment=F}
source("helpers/useful.R")
library(dplyr)
library(magrittr)
```

## Load data

```{r load data}
df <- read.csv("../data/act-learn-ii-rb-replication.csv", stringsAsFactors = F)
```

## Exclusionary criteria

Overall performance (averaged across blocks) was more than three standard deviations below the mean of their group.

```{r exclusionary}
ss <- df %>%
    filter(trial_type == "test") %>%
    group_by(subids, condition, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high_acc = ci.high(correct),
              ci_low_acc = ci.low(correct))

# get the mean and standard deviation of each group
ms_ss <- ss %>%
    group_by(condition, category_type) %>%
    summarise(group_mean = mean(mean_accuracy),
              group_sd = sd(mean_accuracy))
```

Map means and sd to variables

```{r}
# active rb
mean_act_rb <- filter(ms_ss, condition == "active", category_type == "rule-based")$group_mean
sd_act_rb <- filter(ms_ss, condition == "active", category_type == "rule-based")$group_sd

# active ii
mean_act_ii <- filter(ms_ss, condition == "active", category_type == "information-integration")$group_mean
sd_act_ii <- filter(ms_ss, condition == "active", category_type == "information-integration")$group_sd

# receptive rb
mean_rec_rb <- filter(ms_ss, condition == "receptive", category_type == "rule-based")$group_mean
sd_rec_rb <- filter(ms_ss, condition == "receptive", category_type == "rule-based")$group_sd

# receptive ii
mean_rec_ii <- filter(ms_ss, condition == "receptive", 
                      category_type == "information-integration")$group_mean

sd_rec_ii <- filter(ms_ss, condition == "receptive", 
                    category_type == "information-integration")$group_sd
```

Flag subject means that are +/- 3sd 

```{r}
ss_include <- ss %>%
    mutate(
        include = ifelse(condition == "active" & category_type == "rule-based", 
                         ifelse(mean_accuracy > mean_act_rb + 3 * sd_act_rb | mean_accuracy < mean_act_rb - 3 * sd_act_rb, "remove", "include"),
                         ifelse(condition == "active" & category_type == "information-integration",
                                ifelse(mean_accuracy > mean_act_ii + 3 * sd_act_ii | mean_accuracy < mean_act_ii - 3 * sd_act_ii, "remove", "include"),
                                ifelse(condition == "receptive" & category_type =="rule-based",
                                       ifelse(mean_accuracy > mean_rec_rb + 3 * sd_rec_rb | mean_accuracy < mean_rec_rb - 3 * sd_rec_rb, "remove", "include"),
                                       ifelse(condition == "receptive" & category_type =="information-integration",
                                              ifelse(mean_accuracy > mean_rec_ii + 3 * sd_rec_ii | mean_accuracy < mean_rec_ii - 3 * sd_rec_ii, "remove",
                                                     "include")))))) %>% 
    select(subids, include, condition, category_type, mean_accuracy) 

ss_include %>%
    group_by(condition, include, category_type) %>%
    summarise(n())

# merge with full data frame
df <- left_join(df, select(ss_include, subids, include), by = c("subids", "condition"))

# filter out subjects that are +/- 3sd
df <- df %>% filter(include == "include")
```

## Descriptives

```{r demographics, echo=FALSE}
demo_df <- df %>% 
    distinct(subids) %>% 
    xtabs(formula = ~ condition + category_type + order) %>% 
    as.data.frame() %>% 
    rename(count = Freq)

demo_df <- df %>% 
    group_by(subids, condition, category_type, order) %>%
    summarise(exp_length_minutes = sum(rt) / 60000) %>% 
    group_by(condition, category_type) %>% 
    summarise(mean_exp_length = mean(exp_length_minutes)) %>% 
    left_join(demo_df, by = c("condition", "category_type"))
    
knitr::kable(demo_df)
```

## Descriptives

Histogram of length of experiment split by condition 

```{r, echo=F}
ss_rt <- df %>%
    group_by(subids, condition) %>%
    summarise(exp_length_min = sum(rt) / 60000)

qplot(exp_length_min, data=ss_rt, facets=.~condition)
```

```{r}
df %>% 
    group_by(condition, subids) %>% 
    summarise(exp_length_min = sum(rt) / 60000) %>% 
    summarise(mean(exp_length_min))
```

## Overall accuracy analysis 

Get mean accuracy for each condition and category type

```{r, echo=F}
ms <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))

ms_2 <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, category_type, order) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot.

```{r mean acc plot condition/order, echo=F}
a <- qplot(x=category_type, y=mean_accuracy, data=ms,
      geom="bar", stat="identity", fill = condition, position = "dodge") + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6, position=position_dodge(width=0.9)) + 
    scale_fill_brewer(type = "qual", palette = "Set1") +
    coord_cartesian(ylim=c(0.4,1)) +
    ylab("Mean Accuracy") +
    xlab("Category Type") +
    theme(text = element_text(size=16)) +
    geom_hline(yintercept = 0.5) +
    theme_bw() 

b <- qplot(x=category_type, y=mean_accuracy, data=ms_2,
      geom="bar", stat="identity", fill = condition, position = "dodge") + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6, position=position_dodge(width=0.9)) + 
    scale_fill_brewer(type = "qual", palette = "Set1") +
    coord_cartesian(ylim=c(0.4,1)) +
    facet_wrap(~order) +
    ylab("Mean Accuracy") +
    xlab("Category Type") +
    geom_hline(yintercept = 0.5) +
    theme(text = element_text(size=16)) +
    theme_bw() 

gridExtra::grid.arrange(a, b)
```

## Accuracy by block analysis

```{r acc by block, echo=F}
ms_block <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, category_type, block_factor) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot accuracy over blocks

```{r acc by block plot, echo=F}
qplot(x=block_factor, y=mean_accuracy, data=ms_block, color = condition,
      geom=c("point", "line"), stat="identity", linetype = category_type, 
      shape = category_type) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6) + 
    scale_x_discrete() +
    scale_y_continuous(limits=c(0,1)) +
    scale_color_brewer(type = "qual", palette = "Set1") +
    ylab("Mean Accuracy") +
    xlab("Block") +
    theme_classic() +
    theme(text = element_text(size=16))
```

Accuracy by block and dimension.

```{r acc by block and dimension, echo=F}
ms_block <- df %>%
    filter(trial_type == "test") %>%
    group_by(condition, block_factor, order, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high = ci.high(correct),
              ci_low = ci.low(correct))
```

Plot accuracy over blocks

```{r acc by block and dim plot, echo=F}
qplot(x=block_factor, y=mean_accuracy, data=ms_block, color = condition,
      geom=c("point", "line"), stat="identity", facets = order ~ category_type) + 
    geom_linerange(aes(ymin=mean_accuracy - ci_low, 
                       ymax=mean_accuracy + ci_high), 
                   width = .05, size=0.6) + 
    scale_color_brewer(type = "qual", palette = "Set1") +
    scale_y_continuous(limits=c(0,1)) +
    scale_x_discrete() +
    ylab("Mean Accuracy") +
    xlab("Block") +
    theme_bw() +
    theme(text = element_text(size=16))
```

## Evidence selection analysis (active learning)

Analyze the average distance of participants' samples from the optimal decision
boundary.

```{r sampling data, echo=F}
df_sampling <- df %>% filter(condition == "active", trial_type == "training")
```

Rotate, so orientation and radius are on the same dimension.

* dim of interest = dimension with category boundary
* other dim = dimesnion that does not contain the category boundary

```{r rotate samples, echo=F}
df_sampling_rule_based <- df_sampling %>%
    filter(category_type == "rule-based") %>% 
    mutate(category_dimension = ifelse(odb_scale == "orientation_scale",
                                    orientation_response_param,
                                    radius_response_param),
           other_dimension = ifelse(odb_scale == "orientation_scale",
                              radius_response_param,
                              orientation_response_param))

```

Transform information-integration samples

```{r rotate samples ii}
df_sampling_info_integration <- df_sampling %>% 
    filter(category_type == "information-integration")
```

## Plot group level sampling behavior.

```{r sampling plot, fig.width=8}
# Rule-based
a <- qplot(x = category_dimension, y = other_dimension, data = df_sampling_rule_based,
      facets=.~block, color = trial_category) +
    geom_vline(xintercept = 300)

# Information-integration
b <- qplot(x = radius_response_param, y = orientation_response_param, 
           data = filter(df_sampling_info_integration, odb_param == "y>x"),
      facets=.~block, color = trial_category) +
    geom_abline(aes(intercept=0, slope = 1)) 

c <- qplot(x = radius_response_param, y = orientation_response_param, 
           data = filter(df_sampling_info_integration, odb_param == "y<x"),
      facets=.~block, color = trial_category) +
    geom_abline(aes(intercept=600, slope = -1)) 

gridExtra::grid.arrange(a, b, c, ncol = 1)
```

## Plot individual participant sampling behavior

```{r sampling subs, echo=F, fig.width=10}
qplot(x=category_dimension, y=other_dimension, data=filter(df_sampling_rule_based),
      color = as.factor(block_factor)) +
    facet_wrap(~subids) +
    geom_vline(aes(xintercept=300)) 
```


```{r}
e <- qplot(x = radius_response_param, y = orientation_response_param,
      data=filter(df_sampling_info_integration, odb_param == "y>x"),
      color = as.factor(block_factor)) +
    facet_wrap(~subids) +
    geom_abline(intercept = 0, slope = 1) 
    

f <- qplot(x = radius_response_param, y = orientation_response_param,
      data=filter(df_sampling_info_integration, odb_param == "y<x"),
      color = as.factor(block_factor)) +
    facet_wrap(~subids) +
    geom_abline(intercept = 600, slope = -1)

gridExtra::grid.arrange(e, f, ncol = 2)
```

Get distance from optimal decision boundary for each sample.

```{r}
df_sampling_rb <- mutate(df_sampling_rule_based, 
                      samp_dist_odb = ifelse(odb_scale == "orientation",
                                             abs(as.integer(odb_param) - orientation_response_param),
                                             abs(as.integer(odb_param) - radius_response_param))) %>% 
    select(-category_dimension, - other_dimension)

df_sampling_info_integration %<>% 
    mutate(samp_dist_odb = abs(orientation_response_param - radius_response_param))

df_sampling_analysis <- bind_rows(df_sampling_rb, df_sampling_info_integration)
```

Now get the average distance across subjects

```{r}
ms_sampling <- df_sampling_analysis %>%
    group_by(block, category_type) %>%
    summarize(mean_samp_dist = mean(samp_dist_odb),
              ci_high = ci.high(samp_dist_odb),
              ci_low = ci.low(samp_dist_odb))
```

Now plot.

```{r}
qplot(x=block, y=mean_samp_dist, data=ms_sampling, 
      geom="line", ylim=c(75, 280), color = category_type) +
    geom_pointrange(aes(ymin=mean_samp_dist - ci_low, 
                        ymax=mean_samp_dist + ci_high), 
                    width = .05, size=0.6) 
```

Compute average response times across blocks 
for the two different dimensions.  

```{r rt over blocks}
ms_rt <- df_sampling %>%
    group_by(block, category_type) %>%
    summarise(mean_rt = mean(rt),
              ci_high = ci.high(rt),
              ci_low = ci.low(rt))
```

Now plot.

```{r}
qplot(x=as.factor(block), y=mean_rt, data=ms_rt,
      geom="line", color = category_type, group = category_type) +
    geom_pointrange(aes(ymin=mean_rt - ci_low, 
                        ymax=mean_rt + ci_high), 
                    width = .05, size=0.6) 
```

## Plot distribution of test trials

```{r}
df_test_trials <- df %>% filter(trial_type == "test")
```

```{r}
qplot(x = radius_trial_param, y = orientation_trial_param, 
      data = df_test_trials,
      facets=order~category_type, color = trial_category) 
```

## Relationship between sampling and test

Sample distance and accuracy

```{r}
ss_samp_dist <- df_sampling_analysis %>%
    group_by(subids, block, category_type) %>%
    summarise(mean_samp_dist = mean(samp_dist_odb),
              ci_high_msd = ci.high(samp_dist_odb),
              ci_low_msd = ci.low(samp_dist_odb))

ss_mean_acc <- df %>%
    filter(condition == "active", trial_type == "test") %>%
    group_by(subids, block, category_type) %>%
    summarise(mean_accuracy = mean(correct),
              ci_high_acc = ci.high(correct),
              ci_low_acc = ci.low(correct))

# join sampling and test acc together
ss_all <- left_join(ss_samp_dist, ss_mean_acc, by = c("subids" , "block", "category_type"))
```

Plot

```{r}
qplot(x=mean_samp_dist, y=mean_accuracy, facets = category_type ~ block, data=ss_all) +
    geom_smooth(method="lm")
```

## Histogram mean accuracy 

By block

```{r}
qplot(mean_accuracy, facets = block ~ category_type, data = ss_all)
```

Collapsed

```{r}
qplot(mean_accuracy, facets = ~ category_type, data = ss)
```

## LMERs

Model the relationship between mean sampling distance on training trials and mean accuracy
on test trials.

```{r}
m1 <- lm(mean_accuracy ~ mean_samp_dist * block, data=ss_all)
summary(m1)
```

Negative relationship such that those subjects who sampled farther away from the boundary
were less accurate on test, but only in the second active learning block.

Next, we try to predict correct based on condition

```{r}
m2 <- glmer(correct ~ condition * category_type + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 

summary(m2)
```

Effect coding (condition vs. category type) to test main effects.

```{r}
## set vars to factor
df %<>%
    mutate(category_type_factor = as.factor(category_type),
           condition_factor = as.factor(condition))

## effect code (choose contrasts based on how you want to interpret model output)
contrasts(df$category_type_factor) <- cbind("base=rb" = c(1, -1))
contrasts(df$condition_factor) <- cbind("base=passive" = c(1, -1))
```

Model with effect coding. 

```{r}
m3 <- glmer(correct ~ condition_factor * category_type_factor + (1|subids), 
            data=filter(df,trial_type=="test"), family=binomial) 

summary(m3)
```

Intercept is the mean of the means (or the grand mean) of all the groups. These data are unbalanced.
Active better than passive. Information integration worse than rule-based.

# MCF random stuff

```{r}
sdist <- df_sampling_analysis %>%
    group_by(subids) %>%
    mutate(num = 1:n(),
           binned_trial = ceiling(num/8)) %>%
    group_by(subids, binned_trial, condition, category_type) %>%
    summarise(sample_dist_odb = mean(samp_dist_odb))

qplot(binned_trial, sample_dist_odb, 
      group=subids, col = factor(subids), geom="line", 
      data=sdist) + 
    facet_grid(condition~category_type) + 
    geom_smooth(aes(group=1), method="loess", col="black", size = 2)

```
